%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style



\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Sunghyun Kang} % Your name
\address{Ogeum-ro 35-gil 17, Hyundai Apts 26-1102} % Your address
\address{Songpa-gu, Seoul, 05658} % Your secondary addess (optional)
\address{(+82)~10~3217~6864 \\ kanghyun51015@gm.gist.ac.kr} % Your phone number and email
%\address{\bf Nationality: Republic of Korea}
\begin{document}

\textbf{Personal Statement} \\
A committed student who is interested in application of computer science in a real world. Mainly interested in the intersection of these fields.
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Gwangju Institute of Science and Technology(GIST)} \hfill {\em March 2017 - Present} 
\\ Undergraduate, Senior \hfill {Overall GPA: 3.83/4.5} 
\\ Major in Electrical Engineering and Computer Science \hfill  {Major GPA: 4.08/4.5}
\\ Minor in Mathematics

{\bf University of California, Berkeley} \hfill {\em January 2022 - May 2022} 
\\ Berkeley Global Access Program \hfill  {Overall GPA: 3.85/4.0}
\\ Exchange Student of GIST \hfill  {Total Credits: 16}

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages &  Python, MATLAB, R, C, JAVA, C++, Mathematica\\
Software \& Tools & LaTeX, Pytorch, EEGLAB, OR-tools\\
Language & Korean(Native), English(Fluent, iBT TOEFL score of 104) \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience} \itemsep -5pt

\begin{rSubsection}{Data structure and algorithm class at GIST}{September 2018 - October 2018}{Teaching Assistant}{}
\item Marked assignments and held office hours to answer students' questions.
\end{rSubsection}

\begin{rSubsection}{BioComputing Lab at GIST}{May 2021 - December 2021}{Undergraduate Internship}{}
\item Studied on the relationship between Transcranial Direct Current Stimulation (tDCS) applied to Posterior parietal cortex (PPC) and vigilance. Participated in a research to publish a conference paper in IBEC 2021.
\end{rSubsection}

\begin{rSubsection}{CLOUDSTONE Inc.}{June 2022 - Present}{AI Researcher Internship}{}
\item Startup company internship. Usually solving the various VRP(Vehicle Routing Problem) focused on hyper-local service and overall routing service improvement. Also participated in TIPS(Tech Incubator Program for Startup), which is one of the most prestigious fund raising program for technology-based startup in South Korea.
\end{rSubsection}


%------------------------------------------------

\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors \& Scholarship} \itemsep -5pt
\begin{rSubsection}{Government-sponsored Scholarship at GIST}{March 2017 - Present}{}{}
\item Scholarship awarded to most of GIST students by the Korean government.
\end{rSubsection}

\begin{rSubsection}{Scholarship for Summer Session Abroad, UC Berkeley}{June 2018 - August 2018}{}{}
\item Scholarship awarded to students studying abroad during a summer session.
\end{rSubsection}

\begin{rSubsection}{Award from Ministry of Culture, Sports and Tourism \\ Republic of Korea}{December 2019}{}{}
\item Received a prize for the high effort during 2018 Pyeongchang winter Olympic period. Offered for few selected participants who has noticeable achievements.
\end{rSubsection}

\begin{rSubsection}{GIST Academic Scholarship}{March 2021 - Present}{}{}
\item Scholarship awarded to students who showed high achievement in their grades.
\end{rSubsection}

\begin{rSubsection}{GIST Summer Undergraduate Research Fellowship (G-SURF)}{June 2021 - August 2021}{}{}
\item Scholarship awarded to students participating in a summer internship program in GIST.
\end{rSubsection}

\begin{rSubsection}{Scholarship for GIST Study Abroad Program}{January 2022 - May 2022}{}{}
\item Scholarship awarded to students participating in the GIST Study Abroad Program to UC Berkeley or Caltech. Only offered to 10 students per year.
\end{rSubsection}


\end{rSection}

\begin{rSection}{Academic Activities} \itemsep -5pt
\item \textbf{Computational Models of Cognition}: Implemented various cognitive \& language models from the past to the present scheme using MDS(Multidimensional Scaling), MCMC(Markov Chain Monte Carlo), and information theory.
\item \textbf{Probability and Random Process}: Covered from probability scheme such as Bayes rule to various distributions/processes, information theory, Markov chain, hypothesis testing, Hilbert Space and Kalman filter.
\item \textbf{Artificial Intelligence}: Implemented various methods such as searching algorithms, SLAM(Simul-\\-taneous Localization and Mapping), MDP(Markov Deicision Process), and learned basic ML(Machine Learning) and RL(Reinforcement Learning).
\item  \textbf{System Programming}: Implemented a mini shell that is capable of executing commands, redirection, pipe, changing directory, and setting new environment variables.
\item  \textbf{Programming Language and Compilers}: Implemented a lexical analyzer, parser, and semantic analyzer using Lex and Yacc. Made a Makefile compiler \& parser for the final project.
\end{rSection}
%----------------------------------------------------------------------------------------
\begin{rSection}{Relevant Courses}
\itab{\textbf{Major Courses}}  \tab{}  \tab{\textbf{Minor Courses}}
\\ \itab{Computational Models of Cognition} \tab{}  \tab{Numerical Analysis}
\\ \itab{Probability and Random Process} \tab{}  \tab{Graph Theory}
\\ \itab{Introduction to Artificial Intelligence} \tab{}  \tab{Linear algebra and its Application}
\\ \itab{Computer System Theory and Laboratory} \tab{}  \tab{Differential Equations}
\\ \itab{Data structure and algorithms} \tab{} \tab{}
% \\ \itab{Process Control (ongoing)} \tab{} \tab{Electrodynamics}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular} \itemsep -3pt
\begin{rSubsection}{Republic of Korea Air Force}{March 2019 - January 2021}{Reserve Sergeant}{}
\item Mandatory service. Worked as PATRIOT Missile operator, launching sequence simulator maintenance, and technical manual translator.
\end{rSubsection}

\begin{rSubsection}{Wolfram Research Korean Translation Volunteer}{October 2020 - February 2021}{Team Member}{}
\item Participated in Wolfram Research Korean translation team. Focus on translating Mathematica user introduction video, examples, and basic knowledge about overall mathematics.
\end{rSubsection}

\begin{rSubsection}{Brain Power Summer school}{August 2021}{Participant}{}
\item Participated Brain power summer school hosted by Korean society for EEG and Neurophysiology to learn how to handle EEGLAB tools in the actual field studies.
\end{rSubsection}

\begin{rSubsection}{TIPS(Tech Incubator Program for Startup)}{June 2022 - August 2022}{Research Participant \& Presentation}{}
\item Joined TIPS as a participant of Cloudstone Inc. Did a research for company's main technologies(VRP for many(100+) waypoints, Robot based delivery system), made a basis for global strategies, and write a transcript for the presentation.
\end{rSubsection}

\end{rSection}
\end{document}
